Code used to generate paper results : Database comparison and CT characteristics

### 2024-05-16 Paper_code-Database_Comparison.Rmd
Updated database comparison with new CT_genes, changed some database cleaning

@@

```{r Jamin_clean, message = FALSE}
Jamin_core_CT <- read_excel("data/Jamin_core_CT.xlsx")
Jamin_core_CT[Jamin_core_CT$Gene == "KIAA1211", "Gene"] <- "CRACD"
Jamin_core_CT[Jamin_core_CT$Gene == "CXorf67", "Gene"] <- "EZHIP"
```

@@

Wang_CT[Wang_CT$ensembl_gene_id == "ENSG00000181013", "external_gene_name"] <- "C17orf47"
Wang_CT[Wang_CT$ensembl_gene_id == "ENSG00000204293", "external_gene_name"] <- "OR8B2"
Wang_CT[Wang_CT$external_gene_name == "", "external_gene_name"] <- "RNASE11"
Wang_CT[Wang_CT$external_gene_name == "CHCT1", "external_gene_name"] <- "C17orf64"
Wang_CT[Wang_CT$external_gene_name == "PRSS40A", "external_gene_name"] <- "TISP43"
Wang_CT[Wang_CT$external_gene_name == "TEX56P", "external_gene_name"] <- "C6orf201"
Wang_CT[Wang_CT$external_gene_name == "SLC25A51P4", "external_gene_name"] <- "RP11-113D6.10"
Wang_CT[Wang_CT$external_gene_name == "TCP10L3", "external_gene_name"] <- "TCP10"
Wang_CT[Wang_CT$external_gene_name == "SCAND3", "external_gene_name"] <- "ZBED9"
```

@@

Carter_CT[Carter_CT$Gene == "ENSG00000261649", "Gene_Name"] <- "GOLGA6L7"
Carter_CT[Carter_CT$Gene == "ENSG00000239620", "Gene_Name"] <- "PRR20G"
Carter_CT[Carter_CT$Gene == "ENSG00000168148", "Gene_Name"] <- "H3-4"
Carter_CT[Carter_CT$Gene == "ENSG00000204296", "Gene_Name"] <- "TSBP1"
Carter_CT[Carter_CT$Gene == "ENSG00000180219", "Gene_Name"] <- "GARIN6"
Carter_CT[Carter_CT$Gene == "ENSG00000172717", "Gene_Name"] <- "GARIN2"
Carter_CT[Carter_CT$Gene == "ENSG00000174015", "Gene_Name"] <- "CBY2"
Carter_CT[Carter_CT$Gene == "ENSG00000224960", "Gene_Name"] <- "PPP4R3C"
```

@@

lost[lost$external_gene_name == "C21orf59", "Gene_Name"] <- "CFAP298"
lost[lost$external_gene_name == "C11orf57", "Gene_Name"] <- "NKAPD1"
lost[lost$external_gene_name == "C7orf55", "Gene_Name"] <- "FMC1"
lost[lost$external_gene_name == "C10orf12", "Gene_Name"] <- "LCOR"
lost[lost$external_gene_name == "RPL19P12", "Gene_Name"] <- "RPL19P12"
lost[lost$external_gene_name == "C16orf59", "Gene_Name"] <- "TEDC2"
lost[lost$external_gene_name == "TTTY15", "Gene_Name"] <- "USP9Y"
lost[lost$external_gene_name == "C17orf53", "Gene_Name"] <- "HROB"
lost[lost$external_gene_name == "C1orf112", "Gene_Name"] <- "FIRRM"
lost[lost$external_gene_name == "C12orf66", "Gene_Name"] <- "KICS2"
lost[lost$external_gene_name == "C9orf84", "Gene_Name"] <- "SHOC1"
lost[lost$external_gene_name == "C10orf25", "Gene_Name"] <- "ZNF22-AS1"
lost[lost$external_gene_name == "C20orf197", "Gene_Name"] <- "LINC02910"
lost[lost$external_gene_name == "C3orf67", "Gene_Name"] <- "CFAP20DC"
lost[lost$external_gene_name == "C8orf37", "Gene_Name"] <- "CFAP418"
lost[lost$external_gene_name == "C22orf34", "Gene_Name"] <- "MIR3667HG"

@@

missing_Bruggeman <- c("BMS1P4", "ADAM6", "ANXA2P3", "ARHGAP11B", "DPY19L2P2", 
                       "HLA-L", "PA2G4P4", "PIPSL", "PRKY", "YBX3P1", 
                       "RPL23AP53", "UQCRBP1", "RPL23P8", "MRS2P2", "PIN4P1", 
                       "SLC6A10P", "GUSBP2", "PPIEL", "LRRC37BP1", "MSL3P1", 
                       "PLEKHA8P1", "STAG3L1", "TCAM1P", "ZNF702P", "ZNF815P", 
                       "ATP6AP1L", "RPL21P44", "SEC14L1P1", "ZNF876P", 
                       "RPLP0P2", "FAM86JP", "FAM175A", "LACE1", "ATP5EP2", 
                       "WDR92", "TCTE3", "METTL20", "KIAA2022", "ZNRD1-AS1", 
                       "SGOL1", "FAM35DP", "MTL5", "TMEM14E", "MLLT4-AS1", 
                       "CCDC173", "KIAA1524", "WDR78", "LINC00476", "LYRM5", 
                       "HILS1", "CASC5", "KIAA1919", "CTAGE5", "FAM188B", 
                       "TMEM194B", "FAM122C", "PPP1R2P3", "KIAA0391", "SGOL2", 
                       "FAM19A3", "ZNF788", "RPL19P12", "FIRRM")

external_names_to_keep <- gene_synonym %>%
   filter(external_synonym %in% missing_Bruggeman) %>%
   filter(!external_gene_name %in% c("ATP5F1EP2", "POLR1HASP", "SHLD2P3", 
                                   "TMEM14EP", "H1-9P", "ZNF788P")) %>% 
   mutate(Gene_Name = external_gene_name)

@@

Bruggeman_CT <- Bruggeman_CT %>% 
  dplyr::select(Gene_Name)
```

@@

```{r CTdatabase_ours}
CTdatabase_ours <- Venn(list(CTdatabase = CTdatabase_cleaned$external_gene_name,
                             CTexploreR = CT_genes$external_gene_name))
gp <- VennThemes(compute.Venn(CTdatabase_ours))
gp[["Face"]][["11"]]$fill <-  "mistyrose"
gp[["Face"]][["01"]]$fill <-  "darkseagreen1"
gp[["Face"]][["10"]]$fill <-  "lightsteelblue1"
gp[["Set"]][["Set1"]]$col <-  "paleturquoise4"
gp[["Set"]][["Set2"]]$col <-  "darkseagreen4"
gp[["SetText"]][["Set1"]]$col <-  "paleturquoise4"
gp[["SetText"]][["Set2"]]$col <-  "darkseagreen4"
plot(CTdatabase_ours, gp = gp)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Venn_CTdatabase.pdf"))
plot(CTdatabase_ours, gp = gp)
dev.off()
```

@@

```{r CTdatabase_lost}
CTdatabase_lost <- all_genes %>%
  filter(external_gene_name %in% CTdatabase_ours@IntersectionSets[["10"]])

# 9 Genes are lost because not in any database

@@

CTdatabase_lost_upset <- 
  list(`Not testis specific` = 
         filter(CTdatabase_lost,
                testis_specificity != "testis_specific")$external_gene_name,
       `Not tumour activated` = 
         filter(CTdatabase_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(CTdatabase_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/upset_CTdatabase_lost.pdf"))
upset(upset_CTdatabase,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r upset_plot}
core_ours <- Venn(list(Jamin = Jamin_core_CT$Gene, 
                       CTexploreR = CT_genes$external_gene_name))

Wang_ours <- Venn(list(Wang = Wang_CT$external_gene_name, 
                       CTexploreR = CT_genes$external_gene_name))

Carter_ours <- Venn(list(Carter_CT = Carter_CT$Gene_Name, 
                         CTexploreR = CT_genes$external_gene_name))

Bruggeman_ours <- Venn(list(Bruggeman = Bruggeman_CT$Gene_Name,
                            CTexploreR = CT_genes$external_gene_name))

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/upset_omics.pdf"))
upset(upset_omics)
dev.off()
```

@@

Jamin_lost <- all_genes %>%
  filter(external_gene_name %in% core_ours@IntersectionSets[["10"]])

@@

Jamin_lost_upset <- 
  list(`Not testis specific` = 
         filter(Jamin_lost,
                testis_specificity != "testis_specific")$external_gene_name,
       `Not tumour activated` = 
         filter(Jamin_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(Jamin_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Venn_Jamin.pdf"))
plot(core_ours, gp = gp)
dev.off()

pdf(file = paste0("figs/upset_Jamin_lost.pdf"))
upset(upset_Jamin,
      text.scale = upset_text_size)
dev.off()
```

@@

Wang_lost <- all_genes %>%
  filter(external_gene_name %in% Wang_ours@IntersectionSets[["10"]])

@@

Wang_lost_upset <- 
  list(`Not testis specific` = 
         filter(Wang_lost,
                testis_specificity != "testis_specific")$external_gene_name,
       `Not tumour activated` = 
         filter(Wang_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(Wang_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Venn_Wang.pdf"))
plot(Wang_ours, gp = gp)
dev.off()

pdf(file = paste0("figs/upset_Wang_lost.pdf"))
upset(upset_Wang,
      text.scale = upset_text_size)
dev.off()
```

@@

Carter_lost <- all_genes %>%
  filter(external_gene_name %in% Carter_ours@IntersectionSets[["10"]])

@@

Carter_lost_upset <- 
  list(`Not testis specific` = 
         filter(Carter_lost,
                testis_specificity != "testis_specific")$external_gene_name,
       `Not tumour activated` = 
         filter(Carter_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(Carter_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Venn_Carter.pdf"))
plot(Carter_ours, gp = gp)
dev.off()

pdf(file = paste0("figs/upset_Carter_lost.pdf"))
upset(upset_Carter,
      text.scale = upset_text_size)
dev.off()
```

@@

Bruggeman_lost <- all_genes %>%
  filter(external_gene_name %in% Bruggeman_ours@IntersectionSets[["10"]])

@@

Bruggeman_lost_upset <- 
  list(`Not testis specific` = 
         filter(Bruggeman_lost,
                testis_specificity != "testis_specific")$external_gene_name,
       `Not tumour activated` = 
         filter(Bruggeman_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(Bruggeman_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Venn_Bruggeman.pdf"))
plot(Bruggeman_ours, gp = gp)
dev.off()

pdf(file = paste0("figs/upset_Bruggeman_lost.pdf"))
upset(upset_Bruggeman,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r all_databases}
common <- unique(c(core_ours@IntersectionSets[["11"]], 
                   CTdatabase_ours@IntersectionSets[["11"]], 
                   Wang_ours@IntersectionSets[["11"]], 
                   Carter_ours@IntersectionSets[["11"]],
                   Bruggeman_ours@IntersectionSets[["11"]]))

@@

lost_list <- unique(c(core_ours@IntersectionSets[["10"]],
                      CTdatabase_ours@IntersectionSets[["10"]],
                      Wang_ours@IntersectionSets[["10"]],
                      Carter_ours@IntersectionSets[["10"]],
                      Bruggeman_ours@IntersectionSets[["10"]]))

@@

all_lost_upset <- 
  list(`Not testis specific` = 
         filter(lost,
                testis_specificity != "testis_specific")$external_gene_name,
       `Not tumour activated` = 
         filter(lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/upset_all_lost.pdf"))
upset(upset_all,
      text.scale = upset_text_size)
dev.off()
```

>>>>

CTdatabase_cleaned <- CTdatabase_cleaned[!duplicated(CTdatabase_cleaned$external_gene_name), ]

length(CTdatabase_cleaned$ensembl_gene_id[!CTdatabase_cleaned$ensembl_gene_id%in%all_genes$ensembl_gene_id])
```

9 genes are not found in all_genes even when using gene names and ensembl_gene_id

@@

```{r Jamin_clean, message = FALSE}
Jamin_core_CT <- read_excel("data/Jamin_core_CT.xlsx")
Jamin_core_CT[Jamin_core_CT$Gene == "KIAA1211", "Gene"] <- "CRACD"
Jamin_core_CT[Jamin_core_CT$Gene == "CXorf67", "Gene"] <- "EZHIP"
Jamin_core_CT[Jamin_core_CT$Gene == "KIAA1109", "Gene"] <- "BLTP1"
Jamin_core_CT[Jamin_core_CT$Gene == "C10orf82", "Gene"] <- "SPMIP5"
Jamin_core_CT[Jamin_core_CT$Gene == "TTC30B", "Gene"] <- "IFT70B"
Jamin_core_CT[Jamin_core_CT$Gene == "TTC30A", "Gene"] <- "IFT70A"
```

All gene names have been linked to the right name in all_genes

@@

Wang_CT[Wang_CT$ensembl_gene_id == "ENSG00000181013", "external_gene_name"] <- "C17orf47"
Wang_CT[Wang_CT$ensembl_gene_id == "ENSG00000204293", "external_gene_name"] <- "OR8B2"

length(Wang_CT$external_gene_name[!Wang_CT$external_gene_name %in% all_genes$external_gene_name])
```

12 genes are not found in all_genes, by gene names or ensemble gene id and no 
other name.

@@

Carter_CT[Carter_CT$Gene == "ENSG00000261649", "Gene_Name"] <- "GOLGA6L7"
Carter_CT[Carter_CT$Gene == "ENSG00000239620", "Gene_Name"] <- "PRR20G"
Carter_CT[Carter_CT$Gene == "ENSG00000168148", "Gene_Name"] <- "H3-4"
Carter_CT[Carter_CT$Gene == "ENSG00000204296", "Gene_Name"] <- "TSBP1"
Carter_CT[Carter_CT$Gene == "ENSG00000180219", "Gene_Name"] <- "GARIN6"
Carter_CT[Carter_CT$Gene == "ENSG00000172717", "Gene_Name"] <- "GARIN2"
Carter_CT[Carter_CT$Gene == "ENSG00000174015", "Gene_Name"] <- "CBY2"
Carter_CT[Carter_CT$Gene == "ENSG00000224960", "Gene_Name"] <- "PPP4R3C"
Carter_CT[Carter_CT$Gene == "ENSG00000221843", "Gene_Name"] <- "SPATA31H1"
Carter_CT[Carter_CT$Gene == "ENSG00000177947", "Gene_Name"] <- "CIMAP1A"
Carter_CT[Carter_CT$Gene == "ENSG00000172073", "Gene_Name"] <- "SPMIP9"
Carter_CT[Carter_CT$Gene == "ENSG00000229894", "Gene_Name"] <- "GK3"
Carter_CT[Carter_CT$Gene == "ENSG00000249693", "Gene_Name"] <- "SPMAP2L"
Carter_CT[Carter_CT$Gene == "ENSG00000173728", "Gene_Name"] <- "SPMIP3"

length(Carter_CT$Gene[!Carter_CT$Gene %in% all_genes$ensembl_gene_id])

1 gene cannot be found in all_genes even by ensemble or gene name

@@

lost[lost$external_gene_name == "C21orf59", "Gene_Name"] <- "CFAP298"
lost[lost$external_gene_name == "C11orf57", "Gene_Name"] <- "NKAPD1"
lost[lost$external_gene_name == "C7orf55", "Gene_Name"] <- "FMC1"
lost[lost$external_gene_name == "C10orf12", "Gene_Name"] <- "LCOR"
lost[lost$external_gene_name == "RPL19P12", "Gene_Name"] <- "RPL19P12"
lost[lost$external_gene_name == "C16orf59", "Gene_Name"] <- "TEDC2"
lost[lost$external_gene_name == "TTTY15", "Gene_Name"] <- "USP9Y"
lost[lost$external_gene_name == "C17orf53", "Gene_Name"] <- "HROB"
lost[lost$external_gene_name == "C1orf112", "Gene_Name"] <- "FIRRM"
lost[lost$external_gene_name == "C12orf66", "Gene_Name"] <- "KICS2"
lost[lost$external_gene_name == "C9orf84", "Gene_Name"] <- "SHOC1"
lost[lost$external_gene_name == "C10orf25", "Gene_Name"] <- "ZNF22-AS1"
lost[lost$external_gene_name == "C20orf197", "Gene_Name"] <- "LINC02910"
lost[lost$external_gene_name == "C3orf67", "Gene_Name"] <- "CFAP20DC"
lost[lost$external_gene_name == "C8orf37", "Gene_Name"] <- "CFAP418"
lost[lost$external_gene_name == "C22orf34", "Gene_Name"] <- "MIR3667HG"
lost[lost$external_gene_name == "C9orf131", "Gene_Name"] <- "SPATA31G1"

@@

missing_Bruggeman <- Bruggeman_CT[!Bruggeman_CT$Gene_Name %in% 
                                    all_genes$external_gene_name, ]$Gene_Name

external_names_to_keep <- gene_synonym %>%
   filter(external_synonym %in% missing_Bruggeman) %>%
   filter(external_gene_name %in% all_genes$external_gene_name) %>% 
   mutate(Gene_Name = external_gene_name)

@@

Bruggeman_CT <- Bruggeman_CT %>% 
  dplyr::select(Gene_Name)

length(Bruggeman_CT$Gene_Name[!Bruggeman_CT$Gene_Name %in% 
                                all_genes$external_gene_name])
```

38 genes are not found with their names in all genes

@@

```{r CTdatabase_ours}
CTdatabase_ours <- Venn(list(CTexploreR = CT_genes$external_gene_name,
                             CTdatabase = CTdatabase_cleaned$external_gene_name))
gp <- VennThemes(compute.Venn(CTdatabase_ours))
gp[["Face"]][["11"]]$fill <-  "mediumaquamarine"
gp[["Face"]][["10"]]$fill <-  "darkseagreen1"
gp[["Face"]][["01"]]$fill <-  "lightsteelblue1"
gp[["Set"]][["Set2"]]$col <-  "paleturquoise4"
gp[["Set"]][["Set1"]]$col <-  "darkseagreen4"
gp[["SetText"]][["Set2"]]$col <-  "paleturquoise4"
gp[["SetText"]][["Set1"]]$col <-  "darkseagreen4"
plot(CTdatabase_ours, gp = gp)

@@

@@

```{r CTdatabase_lost}
CTdatabase_lost <- all_genes %>%
  filter(external_gene_name %in% CTdatabase_ours@IntersectionSets[["01"]])

# 9 Genes are lost because not in any database like before

@@

CTdatabase_lost_upset <- 
  list(`Not testis specific` = 
         filter(CTdatabase_lost,
                testis_specificity != "testis_specific" & 
                  CT_gene_type == "other")$external_gene_name,
       `Not tumour activated` = 
         filter(CTdatabase_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(CTdatabase_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/CTdatabase_comparison.pdf"))
plot(CTdatabase_ours, gp = gp)
upset(upset_CTdatabase,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r upset_plot}
core_ours <- Venn(list(CTexploreR = CT_genes$external_gene_name,
                       Jamin = Jamin_core_CT$Gene))

Wang_ours <- Venn(list(CTexploreR = CT_genes$external_gene_name,
                       Wang = Wang_CT$external_gene_name))

Carter_ours <- Venn(list(CTexploreR = CT_genes$external_gene_name,
                         Carter_CT = Carter_CT$Gene_Name))

Bruggeman_ours <- Venn(list(CTexploreR = CT_genes$external_gene_name,
                            Bruggeman = Bruggeman_CT$Gene_Name))

@@

@@

Jamin_lost <- all_genes %>%
  filter(external_gene_name %in% core_ours@IntersectionSets[["01"]])

@@

Jamin_lost_upset <- 
  list(`Not testis specific` = 
         filter(Jamin_lost,
                testis_specificity != "testis_specific" &
                  CT_gene_type == "other")$external_gene_name,
       `Not tumour activated` = 
         filter(Jamin_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(Jamin_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Jamin_comparison.pdf"))
plot(core_ours, gp = gp)
upset(upset_Jamin,
      text.scale = upset_text_size)
dev.off()
```

@@

Wang_lost <- all_genes %>%
  filter(external_gene_name %in% Wang_ours@IntersectionSets[["01"]])

# 12 genes lost because no info like before

@@

Wang_lost_upset <- 
  list(`Not testis specific` = 
         filter(Wang_lost,
                testis_specificity != "testis_specific" &
                  CT_gene_type == "other")$external_gene_name,
       `Not tumour activated` = 
         filter(Wang_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(Wang_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Wang_comparison.pdf"))
plot(Wang_ours, gp = gp)
upset(upset_Wang,
      text.scale = upset_text_size)
dev.off()
```

@@

Carter_lost <- all_genes %>%
  filter(external_gene_name %in% Carter_ours@IntersectionSets[["01"]])

# 1 lost because no info, like before

@@

Carter_lost_upset <- 
  list(`Not testis specific` = 
         filter(Carter_lost,
                testis_specificity != "testis_specific" &
                  CT_gene_type == "other")$external_gene_name,
       `Not tumour activated` = 
         filter(Carter_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(Carter_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Carter_comparison.pdf"))
plot(Carter_ours, gp = gp)
upset(upset_Carter,
      text.scale = upset_text_size)
dev.off()
```

@@

Bruggeman_lost <- all_genes %>%
  filter(external_gene_name %in% Bruggeman_ours@IntersectionSets[["01"]])

# 38 lost, like before

@@

Bruggeman_lost_upset <- 
  list(`Not testis specific` = 
         filter(Bruggeman_lost,
                testis_specificity != "testis_specific" &
                  CT_gene_type == "other")$external_gene_name,
       `Not tumour activated` = 
         filter(Bruggeman_lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(Bruggeman_lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Bruggeman_comparison.pdf"))
plot(Bruggeman_ours, gp = gp)
upset(upset_Bruggeman,
      text.scale = upset_text_size)
dev.off()
```

@@

```{r all_databases}
all_database_gene_list <- list(CTexploreR = CT_genes$external_gene_name,
                               Carter = Carter_CT$Gene_Name,
                               Jamin = Jamin_core_CT$Gene,
                               CTatlas = Wang_CT$external_gene_name,
                               Bruggeman = Bruggeman_CT$Gene_Name,
                               CTdatabase = CTdatabase_cleaned$external_gene_name)

upset_all_database <- fromList(all_database_gene_list)
upset(upset_all_database,
      nsets = 6,
      nintersects = 50,
      text.scale = upset_text_size)

common <- unique(c(core_ours@IntersectionSets[["11"]], 
                   CTdatabase_ours@IntersectionSets[["11"]], 
                   Wang_ours@IntersectionSets[["11"]], 
                   Carter_ours@IntersectionSets[["11"]],
                   Bruggeman_ours@IntersectionSets[["11"]]))

@@

lost_list <- unique(c(core_ours@IntersectionSets[["01"]],
                      CTdatabase_ours@IntersectionSets[["01"]],
                      Wang_ours@IntersectionSets[["01"]],
                      Carter_ours@IntersectionSets[["01"]],
                      Bruggeman_ours@IntersectionSets[["01"]]))

@@

all_lost_upset <- 
  list(`Not testis specific` = 
         filter(lost,
                testis_specificity != "testis_specific" &
                  CT_gene_type == "other")$external_gene_name,
       `Not tumour activated` = 
         filter(lost,
                (TCGA_category != "activated" &
                  TCGA_category != "multimapping_issue")|
                   CCLE_category != "activated")$external_gene_name,
       `CT preferential` =
         filter(lost,
                CT_gene_type == "CTP_gene")$external_gene_name)

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/upset_all_lost.pdf"))
upset(upset_all,
      text.scale = upset_text_size)
dev.off()

pdf(file = paste0("figs/upset_all_databases.pdf"))
upset(upset_all_database,
      nsets = 6,
      nintersects = 50)
dev.off()
```
